Self-assembly of colloid-cholesteric composites: A route to switchable optical materials

### 2013-10-14 papers/2012-sandwich/support.tex
Added E_x-field pics and structure factor
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@2176 40876441-3496-0410-a613-a2fca35b2ae2

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.95\columnwidth]{support-fig7.pdf}
\end{center}
\caption{Panels A and B as for Fig. 3, but with the disclination lines
removed for clarity. Panel C shows the situation when the field is
switched off: a residual anisotropic structure remains which reflects the
structure induced by the electric field. The electric field direction
when switched on (panel B) is into the plane of the paper.}
\end{figure}

>>>>

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.95\columnwidth]{support-fig7.pdf}
\end{center}
\caption{Panels A and B as for Fig. 3, but with the disclination lines
removed for clarity. Panel C shows the situation when the field is
switched off: a residual anisotropic structure remains which reflects the
structure induced by the electric field. The electric field direction
when switched on (panel B) is into the plane of the paper and along z.}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.24\columnwidth]{support-fig8a.png}
\includegraphics[width=0.24\columnwidth]{support-fig8b.png}
\includegraphics[width=0.24\columnwidth]{support-fig8c.png}
\includegraphics[width=0.24\columnwidth]{support-fig8d.png}
\end{center}
\caption{Particle distribution for switched electric field direction: 
The field is now oriented along x (it was oriented along z in Fig.7 and Fig.3 main article). 
The leftmost panel shows the configuration with the disclination lines removed 
for clarity. The centre left picture shows the Fourier transform of the colloids for   
wavevectors $k_y, k_z\in [-3\pi/8,3\pi/8]$. The centre right panels depicts the residual 
anisotropy after switch off.}
\end{figure}
